---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bigcurve

<!-- badges: start -->
[![R-CMD-check](https://github.com/hypertidy/bigcurve/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/bigcurve/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of bigcurve is to adaptively densify lines: insert vertices along
great circle arcs exactly where a map projection bends them, and nowhere
else. This is the adaptive resampling scheme of d3-geo by Mike Bostock,
brought to R for paths and for segment meshes.

The error is controlled in the plane of the target projection: straight
chords drawn between output vertices stay within `tolerance` (in projected
units) of the true projected curve. By default the tolerance is derived
from the projected extent, "about one part in 2048 of the plot".

## Installation

You can install the development version of bigcurve like so:

``` r
install.packages("bigcurve", repos = c("https://hypertidy.r-universe.dev", "https://cloud.r-project.org"))
```

You will need the PROJ development library (`libproj-dev` on
Debian/Ubuntu, `proj-devel` on Fedora, `proj` from Homebrew); Windows and
recent Rtools have PROJ built in.

## Example

We get *just enough* points to carry the curvature of a line from point A
to point B (the shortest great circle distance) into a projection.

```{r example}
library(bigcurve)
crs <- "+proj=tmerc +lon_0=147 +lat_0=-42"
s <- segment(c(140, -164), c(-89, 80))
d <- densify(s, crs)
dim(d)

op <- par(mfrow = c(2, 1), mar = rep(0.2, 4))
m <- do.call(cbind, maps::map(plot = FALSE)[1:2])
plot(d, type = "l"); lines(m); axis(1); axis(2)
text(s, lab = c("A", "B"), pos = 2)
plot(rproj_xy(d, crs), type = "l", asp = 1)
plot(rproj_xy(d, crs), type = "p", asp = 1)

points(rproj_xy(m, crs), pch = ".")
axis(1); axis(2)
par(op)
```

The same path in a different projection is the *same path*, densified
differently, because the curvature is a different situation there.

```{r different}
crs2 <- "+proj=stere +lon_0=180 +lat_0=20"
d2 <- densify(s, crs2)
plot(rproj_xy(d2, crs2), type = "l", asp = 1)
points(rproj_xy(m, crs2), pch = ".")
```

## Graticules

`densify()` also works on segment meshes (rgl mesh3d style, `vb` vertices
and `is` segment indices), so a whole graticule refines in one call.
`textures::segs()` builds one and textures provides the 2D mesh plot.

```{r graticule}
library(textures)
prj <- "+proj=laea +lat_0=-60"
mesh <- segs(c(40, 20), extent = c(-180, 180, -65, 65))
out <- densify(mesh, prj)
c(input = ncol(mesh$vb), output = ncol(out$vb))

## project the refined mesh for display
out$vb[1:2, ] <- t(rproj_xy(t(out$vb[1:2, , drop = FALSE]), prj))
plot(out, asp = 1)
points(t(out$vb[1:2, ]))
```

## Notes

Output coordinates are in the source coordinate system (geographic by
default); project them for plotting, as above. Points that cannot be
projected (beyond the horizon of an orthographic projection, say) never
error: their segments are simply left alone, clipping is a job for
another package.

The proper source of goodness is here:

<https://bost.ocks.org/mike/example/>

---

## Code of Conduct

Please note that the bigcurve project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
