---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bigcurve

<!-- badges: start -->
<!-- badges: end -->

The goal of bigcurve is to adaptively densify lines. Like D3's Flawed Example by Mike Bostock. 

Very WIP, very slow, very messy. Don't use. 

Get in touch if you're interested!  Post [an issue to discuss](https://github.com/hypertidy/bigcurve/issues) or ping me [on twitter](https://twitter.com/mdsumner). 


## Installation

You can install the development version of bigcurve like so:

``` r
devtools::install_github("hypertidy/bigcurve")
```

## Example

This is a basic example which shows you how to solve a common problem. 

What's the point? We get *just enough* points to carry the curvature of our
line from point A to point B (shown in the longlat map) over the shortest distance. 

The `dist` argument controls the minimum distance, but be aware this is very slow and flaky for now. 

```{r example}
library(bigcurve)
s <- segment(c(140, -164), c(-89, 80))
#crs <- laea(runif(1, -180, 180), runif(1, -90, 90))
#crs <- "+proj=omerc +lon_0=147 +lonc = 180 +gamma=10 +lat_0=-42"
crs <- "+proj=tmerc +lon_0=147 +lat_0=-42"
par(mfrow = c(2, 1), mar = rep(0.1, 4))
plot(s);maps::map(add = T);axis(1);axis(2)
plot(ss <- sf::st_transform(bigcurve:::bisect(s, crs, dist = 3e4), crs))
xy <- do.call(cbind, maps::map(plot = FALSE)[1:2])
points(sf::sf_project("OGC:CRS84", crs, xy), pch = ".")
axis(1);axis(2)
points(sf::st_coordinates(ss)[, c("X", "Y")])

```


The proper source of goodness is here:

https://bost.ocks.org/mike/example/


---

## Code of Conduct
  
Please note that the bigcurve project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
